\documentclass[11pt]{article}
\usepackage{bookmark}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{color}
\usepackage{comment}
\usepackage{float}
\usepackage{graphicx}
%\usepackage[hidelinks]{hyperref}
\usepackage{makecell}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage{wrapfig}
\usepackage{url}
\usepackage[table]{xcolor}
\graphicspath{{images/}}
\setlength{\parindent}{0.25in}
\setlength{\parskip}{.05in}
\pagestyle{plain}
%Title, date an author of the document
\title{Progress Report}
\author{Bardia Mojra}


\begin{document}
\maketitle
\thispagestyle{empty}

\bigskip
\bigskip
\begin{center}
 Robotic Vision Lab
\end{center}

\begin{center}
The University of Texas at Arlington
\end{center}

\newpage



\section{Progress}
The following items are listed in the order of priority:
\begin{itemize}
  \item DLO Dataset (\textcolor{red}{IROS - March 1st.}): Last night, I was able
  to test the RealSense+UR5e data collection system in operation mode. I need to
  disable the watchdog timer, and UR5e will run properly, but I rather keep it or
  replace it with a similar safety feature. The code is developed based on
  the latest versions of OpenCV, RealSense, and UR5e Python API, making it useful
  for further development for at least five years. Moreover, the code
  is objected-oriented and coding-standard compliant, making it portable,
  modular, and easy to integrate into various applications. It can easily support
  multiple dataset papers. rsDevice module is the object-oriented implementation of
  RealSense API that currently supports RGBD capture, alignment, depth clipping,
  decimation, filtering, save-to-file, live 2D view, point cloud generation,
  bag file parser (rsParser Module), and more. The implementation supports
  expansion to all available features provided by the manufacturer. While working
  on the rsDevice module, I learned the original C++ implementation of the
  RealSense API is buggy and requires special care while handling. C++ does not
  have built-in garbage collection at the compiler level nor it provides routines
  such as Malloc() and Calloc() for manual garbage collection. These routines
  were introduced in C11 version of the C language, but I can not recall the same
  for C++. Ultimately, their solution is to run the driver (pipeline) at the
  Kernel level, similar to ROS and in Docker, as everything is contained. My
  solution was to declare RealSense native objects as global objects within the
  rsDevice module. The parser must be a separate module because
  once the pipeline is closed, the deleted RealSense objects linger and do not allow
  a new pipeline to start. Moreover, OpenCV (live-view mode) interferes with
  bag file write operation; recorded bag files will have corrupted indexes.\\
  \item Maicol: \\
  \item DLO Manipulation (\textcolor{red}{IROS}): \cite{abraham2017model}.\\
  \item XEst (\textcolor{red}{RAL ---}): No update.\\
  \end{itemize}

\section{Research Plan}
This section outlines my current research plan for the next 3 months, 6 months,
and 1 year. Moreover, I have included open projects and ideas to keep track of
them.\\
Target conferences: ICRA, IROS (March), CASE (Late Feb.), NIPS.\\
Target Journals: RAL, CVPR, CORAL.\\

\subsection{Research Plan:}
\begin{itemize}
  \item \textbf{3 months:} The primary objective will be to publish the DLO dataset paper,
  (\textcolor{red}{DLO-1}),
  finished my classes, and to meet my next Ph.D. milestone, the comprehensive exam.
  My goal is to submit the DLO dataset paper to IROS by March 1st.\
  \item \textbf{6 months:} Next, I want to explore using DMD as a method to retrieve the
  correct Quaternion solution for the QuEst method, (\textcolor{red}{QuEst-01}).
  I believe this testing this
  is fairly fast and I should be able to publish that paper fairly quickly. I
  believe the RAL would be an appropriate journal to target; we can discuss
  this further with Dr. Gans to get his input.\
  \item \textbf{1 year:} Next, I want to focus on (\textcolor{red}{PIKO-01}) as a method
  for fast online system identification. My aim is to confirm this method by
  comparing it against existing Koopman-based methods. In the following work, I
  will extend this method to control DLOs in real time (\textcolor{red}{DLO-02}).\
\end{itemize}

\subsection{Research Pipeline:}
\begin{itemize}
  \item DLO-01 (\textcolor{red}{IROS - March 1st, 2023}):
  DLO manipulation dataset with DLO configuration and gripper pose, as well
  as the gripper control input. Ideally, UR5 back-EMF current and bus voltage
  should be recorded. A DLO mount is introduced. A method for configuration
  estimation is introduced. Perhaps, a method for learning DLO dynamic can be
  trained and introduced.\
  \item QuEst-01 (\textcolor{red}{IROS}):
  Optimal transform solution for QuEst based on dominant mode decomposition (DMD).
  \item PIKO-01 (\textcolor{red}{TBD}):
  This work leverages DMD and Physics-Informed machine learning to extract
  low-dimensional coherent modal structures from dynamic data. This method
  will extend DMD-based approaches to include mixed basis functions. Moreover,
  this method will automatically try to find the best fit at a specified range
  of ranks. This method will be validated by comparing it against the existing
  Koopman-based MPC control schemes for VTOL-DIP method and introducing a method
  for controlling VTOL-TIP in simulation.
  This method will become the backbone of my Koopman-based MPC
  control research effort.\
  \item DLO-02 (\textcolor{red}{TBD}):
  This method will extend PIKO-01 to a control method for the DLO-01 dataset.

\end{itemize}
  \newpage

%Sets the bibliography style to UNSRT and import the
\newpage
\bibliography{ref}
\bibliographystyle{ieeetr}

\end{document}
