\documentclass[11pt]{article}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{color}
\usepackage{comment}
\usepackage{float}
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage{makecell}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage{wrapfig}
\usepackage{url}
\usepackage[table]{xcolor}

\setlength{\parindent}{0.25in}
\setlength{\parskip}{.05in}
\pagestyle{plain}

%Title, date an author of the document
\title{Progress Report}
\author{Bardia Mojra}

\begin{document}
	\maketitle
	\thispagestyle{empty}



\section{Progress}
\begin{itemize}
  \item Read [1] and [2], set up the environment on my PC. Began working on Image Registration for super resolution project. Nolan has been very helpful. There is a lot to absorb here specially on the theoretical side. 
  
  \item Set up a repository for super resolution project on OneDrive, that way Nolan and I can work together remotely. 
  
  \item Looked into thermal cameras and became familiar with what ICI, FLIR and Optris have to offer. Reached out to ICI and asked for API document and quotes on several items. Still waiting for a complete answer, this is not a good sign.  
  
  \item In order to funding for this semester, I have reached out Dr. Khalili, Dr. Gibbs, Dr. Russell, Dr. Magnusson, Dr. Ahmad, Dr. McMurrough, Dr. Guy, CSE Department, and EE Department with no avail so far. 
\end{itemize}

\section{Plans}

Continue to learn Nolan's code, now that I have access and can develop on my own branch I will comment his code and run it by him to make sure I understand it correctly. 

There many common acronyms used in papers referring to known and useful algorithms. I will make list of them and begin investigating learning one by one. 

Get more comfortable with Python and Numpy. 

Begin working on SLAM. 

Learn ROS. \cite{FiniteImReg}

Apply for scholarships. 

Follow up with residency status, I need to make it in-state. I am currently out-of-state. I cant afford out-of-state and might have defer admission.



%Sets the bibliography style to UNSRT and imports the 
%bibliography file "samples.bib".
%\bibliographystyle{unsrt}
%\bibliography{sample}
\newpage 
\bibliography{bibfile_bm} 
\bibliographystyle{ieeetr}

\end{document}
